%\documentclass[11pt,a4paper]{article}
\documentclass[10pt]{article}

\def\name{Yonatan Berman}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{enumitem} % Enumerate with [resume] option
\usepackage{sectsty} % Custom section fonts
\usepackage{setspace}
\usepackage{titlesec}
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesection}{1em}{}

%\renewcommand{\familydefault}{\sfdefault}
%\usepackage{helvet}

% Body
%\setmainfont{Garamond Premier Pro}

% Title
%\newfontfamily\titleface{Chaparral Pro Subhead}
%\newcommand{\titlefont}[1]{{\titleface\large\MakeUppercase{#1}}}

% Section Headings
%\newfontfamily\sectionface{Chaparral Pro Subhead}
%\sectionfont{\sectionface\mdseries\normalsize\uppercase}
%\subsectionfont{\sectionface\mdseries\normalsize\itshape}

% Other possible font commands include:
% \ttfamily for teletype,
%\sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics,inequality,income distribution},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  left=1in,
  right=1in,
  bottom=1in,
  top=1in
}

%\onehalfspacing
%\singlespacing
\linespread{0.9}

\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
      \setlength{\leftmargin}{1.0em}
      \setlength{\itemsep}{0.1em}
      \setlength{\parskip}{0pt}
      \setlength{\parsep}{0.2em}
    }
}{
  \end{list}
}
\setlist[enumerate]{itemsep=0.2em}

% Print the month and year
\renewcommand{\today}{\ifcase \month \or January\or February\or March\or April\or May%
\or June\or July\or August\or September\or October\or November\or December\fi%
\space \number \year}

\begin{document}

% Place name at left and date at right
{\textbf{\large\MakeUppercase{Yonatan Berman}}}

% Alternatively, print name centered and bold:
%\centerline{\titlefont{\name}}

% Date
\bigskip
%\today

% Contact Information
\bigskip
%\begin{minipage}[t]{0.495\textwidth}
%  The Graduate Center, CUNY \\
%  365 Fifth Avenue, Room 5324 \\
%  New York, NY 10016 \\
%  United States \\
%  \\
%  Phone: +1 212-817-7964 / +44 7490 427676 \\
%  Email: \href{mailto:yberman@gc.cuny.edu}{yberman@gc.cuny.edu} \\
%  Homepage: \href{http://www.yonatanberman.com/}{www.yonatanberman.com}
%\end{minipage}
\begin{minipage}[t]{0.495\textwidth}
  London Mathematical Laboratory \\
  8 Margravine Gardens \\
  London W6 8RH \\
  United Kingdom \\
\end{minipage}
\begin{minipage}[t]{0.495\textwidth}
  Email: \href{mailto:y.berman@lml.org.uk}{y.berman@lml.org.uk}\,;\,\,\,\href{mailto:yberman@gc.cuny.edu}{yberman@gc.cuny.edu}\\
  Homepage: \href{http://www.yonatanberman.com/}{www.yonatanberman.com}
\end{minipage}

\section*{Academic Positions}

\begin{itemize}
\item Paris School of Economics
  \begin{itemize}
  \item Chateaubriand Postdoctoral Fellow, 2017 -- 2018
  \item WID.world Fellow, 2018 --
  \end{itemize}
\item London Mathematical Laboratory
  \begin{itemize}
  \item Fellow, 2018 --
  \end{itemize}
\item City University of New York / Stone Center on Socio-Economic Inequality
  \begin{itemize}
  \item Visiting Associate Professor, 2020
  \item Distinguished Visiting Fellow, Advanced Research Collaborative, 2020
  \end{itemize}
\end{itemize}

\section*{Education}

\begin{itemize}
  \item 2018~~Ph.D., Tel Aviv University
    % Received May 16, 2010
%    \begin{itemize}
%    \item Dissertation Title: ``Stochastic Modeling of Inequality in Complex Financial and Economic Systems''.
%    \item Committee: Han Hong (co-chair), Shakeeb Khan (co-chair), Paul Ellickson, Andrew Sweeting.
%	\item The Wharton School, Visiting Student, 2015--2016.
%	\item University College London, Visiting Student, 2015--2016.
%    \end{itemize}
  \item 2012~~M.Sc. Physics, Ben-Gurion University of the Negev
%    \begin{itemize}
%    \item Dissertation Title: ``A Simplified Spatial Reduced Order Model for Boiling Water Reactor Stability''.
%    \end{itemize}
    % Received May 14, 2006
  \item 2007~~B.Sc. Mathematics and Physics (Talpiot), The Hebrew University of Jerusalem
    % Received May 14, 2004
\end{itemize}

\section*{Research Fields}
\begin{itemize}
\item Economic Inequality, Social Mobility, Political Economy, Decision Theory
\end{itemize}

\section*{Working Papers}
\begin{enumerate}%[resume]
\item \href{https://bit.ly/AbsoluteMobility}{The Long Run Evolution of Absolute Intergenerational Mobility}. \textit{Revise and resubmit, American Economic Journal: Applied Economics}.
\item \href{https://bit.ly/HomoploutiaWIL}{\textit{Homoploutia}: Top Labor and Capital Incomes in the United States, 1950--2020} (with Branko Milanovic).
\item \href{https://bit.ly/DDP_WP}{The Two Growth Rates of the Economy} (with Alex Adamou, and Ole Peters).
\item \href{https://bit.ly/2OgeI8A}{Growth, Inequality and Absolute Mobility in the United States, 1962--2014}.
\item \href{https://bit.ly/2JcKCOc}{On the Link Between Intergenerational Mobility and Inequality: Are They Truly Distinct?}
\item \href{https://bit.ly/2AHQ2vZ}{Microfoundations of Discounting} (with Alex Adamou, Diomides Mavroyiannis, and Ole Peters).
\item \href{https://bit.ly/TimeLotteries}{Risk Preferences in Time Lotteries} (with Mark Kirstein).
\item \href{https://arxiv.org/abs/2005.00056}{What Are We Weighting For? A Mechanistic Model for Probability Weighting} (with Ole Peters, Alex Adamou, and Mark Kirstein).
\item \href{https://bit.ly/COVID_WAGES_Berman}{The Distributional Short-Term Impact of the COVID-19 Crisis on Wages in the United States}.
%\item \href{http://ssrn.com/abstract=2971765}{The Impact of Time Horizon on the Effect of Diversification} (with Ron Berman).
%	\textit{Under review}.
\end{enumerate}

\section*{Work in Progress}
\begin{enumerate}
\item Mobility and Inequality in US Growth, 1968--2018 (with Fran\c{c}ois Bourguignon).
\item Long Run Inequality and Two Types of Intergenerational (Im)mobility (with Ravi Kanbur).
%\item Wealth Inequality in the United States Since 1967: The Role of Income, Saving, Asset Prices and Wealth Mobility.
\end{enumerate}


\section*{Publications}

\begin{enumerate}%[resume]
\item Alvaredo F., Y.~Berman and S.~Morelli \href{http://bit.ly/ABM_NBER}{On the Distribution of Estates and the Distribution of Wealth: Evidence from the Dead} (Chapter forthcoming in NBER book \textit{Measuring and Understanding the Distribution and Intra/Inter-Generational Mobility of Income and Wealth}, eds. Raj Chetty, John N. Friedman, Janet C. Gornick, Barry Johnson, and Arthur Kennickell).
\item Berman Y. \href{http://bit.ly/IsraelPoliticalCleavages}{Inequality, Identity, and the Long-Run Evolution of Political Cleavages in Israel 1949--2019} (Chapter forthcoming in \textit{Political Cleavages, Party Systems and Social Inequalities}, eds. Amory Gethin, Clara Mart\'{i}nez-Toledano, and Thomas Piketty).
\item Berman Y., O.~Peters and A.~Adamou \href{http://bit.ly/2pVXfH8}{Wealth Inequality and the Ergodic Hypothesis: Evidence from the United States}. \textit{Forthcoming in Journal of Income Distribution}.
\item Berman, Y.,  Y.~Shapira and M.~Schwartz (2017).
  \href{http://iopscience.iop.org/article/10.1209/0295-5075/118/38004/meta}{A Fokker-Planck Model for Wealth Inequality Dynamics}.
  \textit{EPL} 118(3), 38004 (\textit{Editor's choice}; also at \href{http://www.europhysicsnews.org/articles/epn/pdf/2017/05/epn2017-48-5-6.pdf}{\textit{Europhysics News highlights} 48(5/6), 14}).
\item Berman, Y.,  Y.~Shapira and M.~Schwartz (2017).
  \href{http://iopscience.iop.org/article/10.1209/0295-5075/116/58003/meta}{Analytical Study of Index-Coupled Herd Behavior in Financial Markets}.
  \textit{EPL} 116(5), 58003.
\item Berman, Y. and Y.~Shapira (2017).
  \href{http://www.sciencedirect.com/science/article/pii/S0378437116307221}{Revisiting $r > g$---The Asymptotic Dynamics of Wealth Inequality}.
  \textit{Physica A} 467, 562--572.
\item Berman, Y. and T.~Aste (2016).
  \href{http://www.sciencedirect.com/science/article/pii/S0378437116303429}{To What Extent Does Immigration Affect Inequality?}
  \textit{Physica A} 462, 1029--1039.
\item Zhang, X., L.~Feng, Y.~Berman, N.~Hu and H.~E.~Stanley (2016).
  \href{http://iopscience.iop.org/article/10.1209/0295-5075/116/18001/meta}{Exacerbated Vulnerability of Coupled Socio-economic Risk in Complex Networks}.
  \textit{EPL} 116(1), 18001.
\item Berman, Y., E.~Ben-Jacob and Y.~Shapira (2016).
  \href{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0154196}{The Dynamics of Wealth Inequality and the Effect of Income Distribution}.
  \textit{PLOS ONE} 11(4), e0154196.
\item Berman, Y., E.~Ben-Jacob, X.~Zhang and Y.~Shapira (2016).
%  \href{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0152487}{Analyzing the Long Term Cohesive Effect of Sector Specific Driving Forces}.
%  \textit{PLOS ONE} 11(3), e0152487.
\item Berman, Y., Y.~Shapira and E.~Ben-Jacob (2015).
  \href{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0130181}{Modeling the Origin and Possible Control of the Wealth Inequality Surge}.
  \textit{PLOS ONE} 10(6), e0130181.
\item Berman, Y., Y.~Shapira and E.~Ben-Jacob (2014).
  \href{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0112427}{Unraveling Hidden Order in the Dynamics of Developed and Emerging Markets''}.
  \textit{PLOS ONE} 9(11), e112427.
\item Shapira Y., Y.~Berman and E.~Ben-Jacob (2014).
  \href{http://iopscience.iop.org/1367-2630/16/5/053040/article}{Modelling the Short Term Herding Behaviour of Stock Markets}.
  \textit{New Journal of Physics} 16, 053040.
%\item Berman, Y. (2013).
%  {An Improved Homogenization Technique for Pin-By-Pin Diffusion Calculations}.
%  \textit{Annals of Nuclear Energy} 53, 238--243.
%\item Berman, Y., Y.~Lederer and E.~Meron (2012).
%  \href{http://www.diva-portal.org/smash/get/diva2:1118961/FULLTEXT01.pdf}{A Simplified Spatial Model for BWR Stability}.
%  \textit{Proceedings of PHYSOR 2012}, 1608--1619.
\end{enumerate}

%\section*{Other Publications}
%
%\begin{enumerate}[resume]
%\item Berman, Y. (2017).
%  \href{http://arxiv.org/abs/1706.07783}{Intergenerational Mobility Measures in a Bivariate Normal Model}.
%  \textit{ArXiv 1706.07783}.
%\item Berman, Y. and T.~Aste (2016).
%  \href{http://ssrn.com/abstract=2803317}{How did EU Immigrants Affect Income and Wealth Inequality in the UK?}
%  \textit{SSRN 2803317}.
%%\item Berman, Y., O.~Peters and A.~Adamou (2016).
%%  \href{http://arxiv.org/abs/1605.05631}{Far from Equilibrium: Wealth Reallocation in the United States}.
%%  \textit{ArXiv 1605.05631}.
%\end{enumerate}
%
\section*{Professional Activities}

\subsection*{Conference Presentations (including scheduled)}

\begin{description}[font=\mdseries]
\item[2021]
  AEA Annual Meeting,
  EE2021 conference,
  Society of Labor Economists Annual Meeting.
\item[2020]
	D-TEA Conference,
	NBER/CRIW Conference on Measuring and Understanding the Distribution and Intra/Inter-Generational Mobility of Income and Wealth.
\item[2019]
  AEA Annual Meeting,
  ECINEQ Meeting 2019,
  EEA-ESEM Annual Congress.
\item[2018]
  Equal Chances Conference,
  French Economic Association Meeting,
  LIS/LWS User Conference.
\item[2017]
  ECINEQ Meeting 2017,
  Econometric Society European Winter Meeting,
  Trends in Inequality: Social, Economic and Political Issues, International Conference on Inequality.
%  Econophysics Colloquium (Warsaw, Poland),
%  NetSci-X (Tel Aviv, Israel).
%\item[2016]
%  The Conference on Complex Systems (Amsterdam, The Netherlands),
%  Non-Stationarity and Ergodicity in Economic and Financial Systems (Amsterdam, The Netherlands),
%  School on Complex Systems (Amsterdam, The Netherlands).
%\item[2015]
%%  Econophysics Colloquium (Prague, Czech Republic),
%  DPG Conference (Berlin, Germany).
%\item[2014]
%  Econophysics Colloquium (Kobe, Japan),
%  International Conference on Econophysics (Shanghai, China).
%\item[2012]
%  PHYSOR (Knoxville, TN),
%  Conference of the Nuclear Societies in Israel (Dead Sea, Israel).
\end{description}

\subsection*{Workshop and Seminar Talks (including scheduled)}

\begin{description}[font=\mdseries]
\item[2021]
    Tel Aviv University,
	University of Haifa.
\item[2020]
	City University of New York,
	Columbia University,
	Rutgers University,
	The University of Edinburgh.
\item[2019]
  City, University of London,
  Columbia University,
  Copenhagen University,
  Freie Universit\"{a}t Berlin,
  Harvard University,
  Norwegian University of Science and Technology,  
  Royal Holloway, University of London,
  Technion -- Israel Institute of Technology,
  Weizmann Institute of Science.
\item[2018]
	London School of Economics,
	Universit\'{e} Paris 1 Panth\'{e}on-Sorbonne,
	University of Haifa,
	The Hebrew University of Jerusalem.
\item[2017]
	London School of Economics,
  	Paris School of Economics,
%  The Institute for Structural Reforms (Tel Aviv, Israel),  
  	Tel Aviv University.
\item[2016]
  Oxford University.
%  NORDITA (Stockholm, Sweden).
\item[2015]
  The Hebrew University of Jerusalem,
  University College London.
%\item[2011]
%  Ben-Gurion University of the Negev (Be'er Sheva, Israel).
\end{description}

\subsection*{Grants, Honors \& Awards}

\begin{itemize}
\item Advanced Research Collaborative Fellowship, 2020
\item Laboratoires d'excellence OSE research grant, 2018 -- 2019
\item Best Junior Scholar Paper, Trends in Inequality: Social, Economic and Political Issues, International Conference on Inequality, 2017
\item Chateaubriand Fellowship, 2017 -- 2018
\item INET Young Scholars Initiative Travel Grant, 2017
\item Dan David Prize Scholarship for Young Researchers -- for Combatting Poverty, 2016 -- 2017
\item Israel Ministry of Science, Technology and Space International PhD Travel Grant, 2016
\item Arie and Ida Crown Memorial Foundation Scholarship, 2015 -- 2016
%\item Econophysics Colloquium 2015 PhD Travel Grant, 2015
\item London Mathematical Laboratory Summer Studentship, 2015
\item Tauber Family Foundation Scholarship, 2014 -- 2016
\item Part of the Head of Israeli Atomic Energy Commission Award Winning Team, 2009
%\item Outstanding Cadet of Class -- Talpiot Program, 2007
%\item Outstanding Cadet of Class -- Talpiot Program, 2006
\end{itemize}

\subsection*{Referee}

Brookings Foreign Policy, Econometrica, Economica, European Economic Review, Journal of Economic Inequality, Journal of Income Distribution, Journal of the European Economic Association, Management Science, Mathematical Social Sciences, PLOS One.

\subsection*{Additional Professional Positions and Visits}

\begin{itemize}
\item World Inequality Database (WID.world)
  \begin{itemize}
  \item Fellow, 2018 --
  \end{itemize}
\end{itemize}

\begin{itemize}
\item Stone Center on Socio-Economic Inequality, City University of New York
  \begin{itemize}
  \item Visiting Scholar, 2018 --
  \end{itemize}
\end{itemize}

\begin{itemize}
\item London Mathematical Laboratory
  \begin{itemize}
  \item Visiting Scholar, 2015 -- 2018
  \end{itemize}
\end{itemize}

%\begin{itemize}
%\item Talpiot Program, Israeli Air Force
%  \begin{itemize}
%  \item Chief Instructor and Deputy Commander, 2012--2013.
%  \end{itemize}
%\end{itemize}

\begin{itemize}
\item Nuclear Research Center -- Negev
  \begin{itemize}
  \item Researcher, 2008 -- 2012
  \end{itemize}
\end{itemize}


%\section*{Professional Activities}
%
%\begin{itemize}
%\item University service:
%  Arts and Sciences Curriculum Committee, SBS Panel (2017--20)
%\item Departmental service:
%  Advisory Committee to the Chair (2017--19),
%  Faculty Recruiting Committee (2010--11, 2011--12, 2014--15, 2016--17, 2017--18),
%  Graduate Studies Committee (2012--13),
%  Graduate Program Review Committee (2013--14),
%  Undergraduate Studies Committee (2014--15),
%  Econometrics seminar organizer (Autumn 2016, Spring 2018),
%  G.S. Maddala Prize Committee (2011, 2012, 2013, 2014, 2015, 2016, 2017).
%\item Member, Econometric Society, 2006--Present.
%\item Member, American Economic Association, 2010--Present.
%\item Member, American Statistical Association, 2011--Present.
%\end{itemize}

%\section*{Advising}
%
%\subsection*{Ph.D. Students, as Primary Advisor (Initial Placement in Parentheses)}
%
%\begin{itemize}
%\item \href{http://chaoma2014.weebly.com}{Chao Ma} (2015, Assistant Professor, Xiamen University, WISE, co-advisor with Donald Haurin)
%\item \href{http://garrettsenney.weebly.com}{Garrett T. Senney} (2016, Financial Economist, Office of the Comptroller of the Currency)
%\item \href{http://junqiushi-ren.weebly.com}{Junqiushi Ren} (2017, Assistant Professor, Southwestern University of Finance and Economics, RIEM) % Research Institute of Economics and Management
%\end{itemize}
%
%\subsection*{Ph.D. Students, as Committee Member}
%
%\begin{itemize}
%\item Chih-Sheng Hsieh (2013, Assistant Professor, Chinese University of Hong Kong)
%\item Chao Yang (2015, Assistant Professor, Shanghai University of Finance and Economics)
%\item Xingbai Xu (2016, Assistant Professor, Xiamen University, WISE)
%\item Xiang Hui (2016, Postdoctoral Researcher, MIT Sloan)
%\item Wei Shi (2016, Assistant Professor, Jinan University Institute for Economic and Social Research)
%\item Kai Yang (2016, Assistant Professor, Shanghai University of Finance and Economics)
%\item Jongwook Park (2017, Economist, Bank of Korea)
%\item Bosung Jang (2017, Economist, Bank of Korea)
%\item Neslihan Sakarya (2017, Assistant Professor, University of Essex)
%\item Tuo Liu (2017, Assistant Professor, Xiamen University, WISE)
%\item Hyewon Kim (2018, expected)
%\item Joseph Rossetti (2018, expected)
%\item Hongyu Chen (2018, expected)
%\item Jon Michel (2019, expected)
%\item Hanbat Jeong (2019, expected)
%\item Bo Wang (2019, expected)
% Seonghoon Kim; candidacy exam, 2011
% Fei Jin; candidacy exam, 2011
% Xi Qu; candidacy exam, 2012
%\end{itemize}
%
%\subsection*{Undergraduate Honors Students}
%
%\begin{itemize}
%\item Erik Lauritzen (2011, co-advisor with Jennifer Suchland)
%\end{itemize}

\section*{Teaching}

\subsubsection*{University of Warwick}

\begin{itemize}
\item Ergodicity in Economics: Spring 2019
\end{itemize}

\subsubsection*{Tel Aviv University}

\begin{itemize}
\item Electricity and Magnetism for Medicine Students: Spring 2014, Spring 2015, Spring 2016, Spring 2017
\item Classical Mechanics for Medicine Students: Autumn 2015, Autumn 2016, Autumn 2017
\end{itemize}

%\subsubsection*{The Hebrew University of Jerusalem}
%
%\begin{itemize}
%\item Talpiot Honors Students Seminar in Physics (lecturer in charge): Spring 2013
%\end{itemize}

\end{document}